\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://jwalton.me/}{\Large Joshua Walton}} & Email : \href{mailto:jswalton.dev@gmail.com}{jswalton.dev@gmail.com}\\
  \href{http://jwalton.me/}{http://www.jwalton.me} & Mobile : +1-843-323-2485 \\
\end{tabular*}

%----------SUMMARY-----------------
\section{Summary}
  \textbf{\normalfont full stack software developer with experience in Java Enterprise technologies, Scala, Play Framework, AngularJS, ReactJS, Amazon Web Services, and mobile. Worked on large enterprise projects and small consumer product projects. Strong communication skills and a desire to engage with fellow team members to collaborate and learn more. Pursuing web application, mobile application, back-end, or full stack development employment opportunities .}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {College of Charleston}{Charleston, SC}
      {Bachelor of Science in Computer Science}{Aug. 2007 -- Dec. 2011}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

      \resumeSubheading
      {Booz Allen Hamilton}{San Diego, CA}
      {Lead Technologist - Sr. Software Engineer}{Jan 2018 - Present}

      \textbf{\normalfont I have worked primarily on APMT(Agile Project Management Tool). APMT is a tool used to visualize and make informed decisions on software development project backlogs.}


      \resumeItemListStart
        \resumeItem{Docker Containerization}
          {Led a refactor effort to containerize project with Docker in order to make product more deployable and decrease developer onboarding times.}
        \resumeItem{Component based architecture refactor}
          {Moved project torwards component based architechture with Spring Boot, Spring Rest Data, ReactJS, Docker, and PostgreSQL in order to move application architecture away from monolithic MVC paradigms.}
        \resumeItem{ReactJS frontend refactor}
          {Refactored frontend user interface from JSP/Jquery to a ReactJS application in order to leverage benefits of top down data flow and component based paradigms.}

      \resumeItemListEnd

    \resumeSubheading
      {Dispute Resolution Data}{Charleston, SC}
      {Software Developer}{Jul 2016 - Present}



      \textbf{\normalfont The mission of Dispute Resolution Data (DRD) is to enhance and grow the field of dispute resolution through access to trusted aggregated data. DRD provides arbitration and mediation institutions the ability to input case data while providing data visualization and tools to data researchers through a SaaS application.}

      \resumeItemListStart
        \resumeItem{AngularJS SPA}
          {Collaborated in the development of a client facing AngularJS application. Data visualization tools developed using hand rolled "widget" library.}
        \resumeItem{Play Framework/Scala API}
          {Developed RESTful API using Scala and Play Framework. }
        \resumeItem{AWS Infrastructure}
          {Deploying and Maintaining application code through Docker containers deployed on AWS ElasticBeanstalk, RDS, S3, SES, Lambda, and Elastic Beanstalk.}
        \resumeItem{NationBuilder Integration}
          {Exposed a client API for accepting pushed changes/ notifications. Integrate with third party RESTful APIs in order to push new user information.}
      \resumeItemListEnd

    \resumeSubheading
      {SPARC, LLC}{Charleston, SC}
      {Software Developer}{Dec 2011 - Jul 2016}



      \textbf{\normalfont I was responsible for the iterative development of new functionality as well as maintenance of existing pieces of VBMS(Veterans Benefits Management System), a Veteran Affairs project, while using agile development methodologies (SCRUM). VBMS is a paperless claims management system that aims to reduce the number of claims in the VA backlog by 2015.}

      \resumeItemListStart
        \resumeItem{SOAP and REST Web Services}
          {Developed API RESTful Web Services for consumption by JQuery front-end. Maintained and developed external SOAP web service interactions.}
        \resumeItem{Letter Correspondence}
          {Integrated external legacy SOAP web services into letter correspondence framework. Tools such as SoapUI and JMockit were used in order to test and develop code to a successful deployment.}
        \resumeItem{Spring Framework}
          {Worked to configure new modules, maintain code, and create new features within spring framework.}
        \resumeItem{PDF Preview Functionality}
          {Developed Servlet to serve byte range requests for PDF documents, enabling PDF Preview functionality to work.}
      \resumeItemListEnd

    \resumeSubheading
      {SPARC, LLC}{Charleston, SC}
      {Intern}{Mar 2011 - Dec 2011}
      \resumeItemListStart
        \resumeItem{Android Development}
          {Developed an Android application to check in office visitors using third-party libraries for facial recognition}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------Languages-----------------
\section{Languages}
  \resumeSubHeadingListStart
    \resumeSubItem{English}
      {Native Language}
    \resumeSubItem{Spanish}
      {Working Proficiency}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
%\section{Programming Skills}
%  \resumeSubHeadingListStart
%    \item{
%      \textbf{Languages}{: Scala, Python, Javascript, C++, SQL, Java}
%      \hfill
%      \textbf{Technologies}{: AWS, Play, React, Kafka, GCE}
%    }
%  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
